### 2012-11-25 paper.tex
added comparison lines

\begin{table}[h]
\centering
\begin{tabular}{llllllll}
	\toprule
									&TP Rate   	&FP Rate   &Precision &Recall  &F-Measure \\
	\midrule
	Decision Tree		\\
  Random Forest		\\
  Naive Bayes			&   0.897  & 0.244   & 0.958     & 0.897  & 0.92     \\
  SVM							&0.959     	&0.959     	&0.919   	&0.959   &0.939    \\
  kNN							&0.959     	&0.959     	&0.919   	&0.959   &0.939    \\
	\bottomrule
\end{tabular}
\caption{Comparison of the different algorithms for the echocardiogram dataset}
\end{table}

>>>>

\begin{table}[h]
\centering
\begin{tabular}{llllllll}
	\toprule
									&TP Rate   	&FP Rate   &Precision &Recall  &F-Measure \\
	\midrule
	Decision Tree &  0.959   & 0.959   & 0.919     & 0.959  & 0.939     &    0.968     \\ 
  Random Forest &		 0.948   &  0.72    &  0.942     &  0.948  &  0.945             \\ 
  Naive Bayes			&   0.897  & 0.244   & 0.958     & 0.897  & 0.92     \\
  SVM							&0.959     	&0.959     	&0.919   	&0.959   &0.939    \\
  kNN							&0.959     	&0.959     	&0.919   	&0.959   &0.939    \\
	\bottomrule
\end{tabular}
\caption{Comparison of the different algorithms for the echocardiogram dataset}
\end{table}
